---
output:
  word_document:
    #reference_docx: styles.docx
  html_document:
    df_print: paged
params:
  site.code: LAKE_P_SUG0011
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(pool)
library(dbplyr)

# Set up database connection
db.params <- readr::read_csv("M:/MONITORING/DS_Water/Data/Database/ConnectFromR/ds-database-conn.csv") %>%
      as.list()
db.params$drv <- odbc::odbc()
conn <- do.call(dbPool, db.params)

# Get spring info from database
spring.info <- tbl(conn, in_schema("export", "SiteInfoSheet")) %>%
  collect() %>%
  filter(SiteCode == params$site.code)

sensorRet.info <- tbl(conn, in_schema("analysis", "SensorRetrievalAttempts")) %>%
  collect() %>%
  filter(SiteCode == params$site.code)

sensorDep.info <- tbl(conn, in_schema("analysis", "SensorsAllDeployments")) %>%
  collect() %>%
  filter(SiteCode == params$site.code)

poolClose(conn)

# Split plot info into visit-level info...
visit.info <- spring.info %>%
  select(-PhotoType, -PhotoLabel, -RenamedFilePath, -UtmX_m, -UtmY_m, -UTMZone, -PhotoNotes) %>%
  unique()

# ...and photo-level info
photo.info <- spring.info %>%
  select(PhotoType, PhotoLabel, RenamedFilePath, UtmX_m, UtmY_m, UTMZone, PhotoNotes) %>%
  mutate(RenamedFilePath = sub("\\\\\\\\INPLAKE52V\\\\ORG", "M:", RenamedFilePath))

photo.types <- c('SOURCE', 'UPSTR', 'DNSTR', 'SENSOR')

photo.info %<>%
  mutate(PhotoType = factor(PhotoType, levels = photo.types)) %>%
  arrange(PhotoType)
```


---
title: `r visit.info$SiteCode`
author: `r visit.info$SiteName`
date: Last visited `r visit.info$VisitDate` (WY `r visit.info$FieldSeason`)
---

**Spring type: ** `r visit.info$SpringType`

**Sample frame: ** `r visit.info$SampleFrame`

**Visit notes: ** `r visit.info$VisitNotes`

**Sensor notes: ** `r visit.info$SensorNotes`

# Deployments
```{r include=FALSE}
dep.section <- NULL
for(row in 1:nrow(sensorDep.info)) {
  dep <- sensorDep.info[row,]
  dep.serialnumber <- dep$SerialNumber
  dep.visitdate <- dep$VisitDate
  dep.notes <- if_else(is.na(dep$Notes), "", paste0(": ", dep$Notes))
  
  dep.section <- c(dep.section, knitr::knit_expand("deployment-info.rmd"), collapse = '\n')
}
```

`r paste(knitr::knit(text = dep.section), collapse = '\n')`

# Photos
```{r include=FALSE}
photo.section <- NULL
for(row in 1:nrow(photo.info)) {
  photo <- photo.info[row,]
  photo.path <- photo$RenamedFilePath
  photo.type <- photo$PhotoType
  photo.label <- photo$PhotoLabel
  utm.x <- photo$UtmX_m
  utm.y <- photo$UtmY_m
  utm.zone <- photo$UTMZone
  photo.notes <- if_else(is.na(photo$PhotoNotes), "", paste0(": ", photo$PhotoNotes))
  
  photo.section <- c(photo.section, knitr::knit_expand("photo-info.rmd"), collapse = '\n')
}
```

`r paste(knitr::knit(text = photo.section), collapse = '\n')`

